---
title: "Readme"
author: "Zilu"
date: "November 20, 2018"
output: html_document
---

# Spectronaut library summary

## Libraries exported from Spectronaut (.xls format)

```{r warning=FALSE}
library(ggplot2)
dir("Spectronaut Library List/Original List")
source("R scripts/Library Filter.R")
reshape2::dcast(LbSum, LBType ~ Type, value.var = 'Numbers')
ggplot(LbSum, aes(x = LBType, y = Numbers, fill = Type)) + geom_bar(stat = "identity", position = position_dodge()) + theme_bw() + geom_text(stat='identity', aes(label= Numbers), vjust= -0.5, nudge_x = c(-0.22, 0.22))
```

### Conclusions
- There are plenty of Tn-peptides in the WT library which were Jacalin enriched
- Tn-library is much larger than T-library after taking Tn-peptides from WT library

## Combined list
- Save in the folder "Spectronaut Library List/Combined List"
- Library Generation.R

```{r}
dir("Spectronaut Library List/Combined List")
```

## Reimport the libraries to Spectronaut and export again
- Save the libraries in "Spectronaut Library List/Combined List/Exported"

```{r warning=FALSE}
dir("Spectronaut Library List/Combined List/Exported")
source("R scripts/Exported Library Filter.R")
reshape2::dcast(LbSum, LBType ~ Type, value.var = 'Numbers')
ggplot(LbSum, aes(x = LBType, y = Numbers, fill = Type)) + geom_bar(stat = "identity", position = position_dodge()) + theme_bw() + geom_text(stat='identity', aes(label= Numbers), vjust= -0.5, nudge_x = c(-0.22, 0.22))
```

## Make in-silico libraries
- Take Serum.xls, Cell_T.xls and Cell_Tn.xls from "Spectronaut Library List/Combined List/Exported"
- Real library is first converted to Tn-library
- Then make T, STn, mST, dST and Naked libraries
- in silico Library.R

## Export the in-silico libraries
- Save in the folder "Spectronaut Library List/in silico library"
- Library Generation.R

```{r}
dir("Spectronaut Library List/in silico library")
```


## Align with the CCG database
- Glycosite Alignment.R
- Take the libraries from "Spectronaut Library List/Combined List/Exported"
- Merge all sequences and align with CCG database

```{r}
source("R scripts/Glycosite Alignment.R")

Cell_T[["Pie"]]
Cell_T[["Bar"]]
Cell_Tn[["Pie"]]
Cell_Tn[["Bar"]]
Serum[["Pie"]]
Serum[["Bar"]]

Aligned.Cell_T[["p"]]
Aligned.Cell_Tn[["p"]]
Aligned.Serum[["p"]]

```



#```{r}
setwd("Figures")
library(VennDiagram)
venn.diagram(list(CCG = unique(AllSites$Sites), Cell_Tn = Cell_Tn[["DF"]]$Sites), filename = "Cell_Tn.png")
venn.diagram(list(CCG = unique(AllSites$Sites), Cell_T = Cell_T[["DF"]]$Sites), filename = "Cell_T.png")
venn.diagram(list(CCG = unique(AllSites$Sites), Serum = Serum[["DF"]]$Sites), filename = "Serum.png")

venn.diagram(list(CCG = unique(AllSites$Sequence), Cell_Tn = Cell_Tn[["DF"]]$Sequence), filename = "Cell_Tn_Sequence.png")
venn.diagram(list(CCG = unique(AllSites$Sequence), Cell_T = Cell_T[["DF"]]$Sequence), filename = "Cell_T_Sequence.png")
venn.diagram(list(CCG = unique(AllSites$Sequence), Serum = Serum[["DF"]]$Sequence), filename = "Serum_Sequence.png")

```

